\subsection{\texttt{CRTM\_Surface\_WriteFile} interface}
  \label{sec:CRTM_Surface_WriteFile_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Surface_WriteFile
 
  PURPOSE:
        Function to write CRTM Surface object files.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_Surface_WriteFile( Filename     , &
                                               Surface      , &
                                               Quiet = Quiet  )
 
  INPUTS:
        Filename:     Character string specifying the name of the
                      Surface format data file to write.
                      UNITS:      N/A
                      TYPE:       CHARACTER(*)
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN)
 
        Surface:      CRTM Surface object array containing the Surface
                      data. Note the following meanings attributed to the
                      dimensions of the Surface array:
                      Rank-1: M profiles.
                              Only profile data are to be read in. The file
                              does not contain channel information. The
                              dimension of the array is understood to
                              be the PROFILE dimension.
                      Rank-2: L channels  x  M profiles
                              Channel and profile data are to be read in.
                              The file contains both channel and profile
                              information. The first dimension of the
                              array is the CHANNEL dimension, the second
                              is the PROFILE dimension. This is to allow
                              K-matrix structures to be read in with the
                              same function.
                      UNITS:      N/A
                      TYPE:       CRTM_Surface_type
                      DIMENSION:  Rank-1 (M) or Rank-2 (L x M)
                      ATTRIBUTES: INTENT(IN)
 
  OPTIONAL INPUTS:
        Quiet:        Set this logical argument to suppress INFORMATION
                      messages being printed to stdout
                      If == .FALSE., INFORMATION messages are OUTPUT [DEFAULT].
                         == .TRUE.,  INFORMATION messages are SUPPRESSED.
                      If not specified, default is .FALSE.
                      UNITS:      N/A
                      TYPE:       LOGICAL
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status: The return value is an integer defining the error status.
                      The error codes are defined in the Message_Handler module.
                      If == SUCCESS, the file write was successful
                         == FAILURE, an unrecoverable error occurred.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
 
  SIDE EFFECTS:
        - If the output file already exists, it is overwritten.
        - If an error occurs during *writing*, the output file is deleted before
          returning to the calling routine.
 
  \end{alltt}
