\subsection{\texttt{CRTM\_AOD} interface}
  \label{sec:CRTM_AOD_interface}
  \begin{alltt}
 
  NAME:
        CRTM_AOD
 
  PURPOSE:
        Function that calculates layer total optical depth profile at nadir.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_AOD( Atmosphere       , &
                                 ChannelInfo      , &
                                 RTSolution       , &
                                 Options = Options  )
 
  INPUTS:
        Atmosphere:     Structure containing the Atmosphere data.
                        UNITS:      N/A
                        TYPE:       CRTM_Atmosphere_type
                        DIMENSION:  Rank-1 (n_Profiles)
                        ATTRIBUTES: INTENT(IN)
 
        ChannelInfo:    Structure returned from the CRTM_Init() function
                        that contains the satellite/sensor channel index
                        information.
                        UNITS:      N/A
                        TYPE:       CRTM_ChannelInfo_type
                        DIMENSION:  Rank-1 (n_Sensors)
                        ATTRIBUTES: INTENT(IN)
 
  OUTPUTS:
        RTSolution:     Structure containing the layer aerosol optical
                        profile for the given inputs.
                        UNITS:      N/A
                        TYPE:       CRTM_RTSolution_type
                        DIMENSION:  Rank-2 (n_Channels x n_Profiles)
                        ATTRIBUTES: INTENT(IN OUT)
 
  OPTIONAL INPUTS:
        Options:        Options structure containing the optional arguments
                        for the CRTM.
                        UNITS:      N/A
                        TYPE:       CRTM_Options_type
                        DIMENSION:  Same as input Atmosphere structure
                        ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status:   The return value is an integer defining the error status.
                        The error codes are defined in the Message_Handler module.
                        If == SUCCESS the computation was sucessful
                           == FAILURE an unrecoverable error occurred
                        UNITS:      N/A
                        TYPE:       INTEGER
                        DIMENSION:  Scalar
 
  COMMENTS:
        - Many of the components of the Options optional input structure
          are not used in this function. Consult the CRTM User Guide for
          which Options components are usable for AOD calculations.
 
  \end{alltt}
