\subsection{\texttt{CRTM\_ChannelInfo\_Subset} interface}
  \label{sec:CRTM_ChannelInfo_Subset_interface}
  \begin{alltt}
 
  NAME:
        CRTM_ChannelInfo_Subset
 
  PURPOSE:
        Function to specify a channel subset for processing in the CRTM.
        By default, ALL channels are processed. This function allows the
        list of channels that are to be processed to be altered.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_ChannelInfo_Subset( ChannelInfo   , &
                                                Channel_Subset, &
                                                Reset           )
 
  OBJECTS:
        ChannelInfo:    Valid ChannelInfo object for which a channel subset is
                        to be specified.
                        UNITS:      N/A
                        TYPE:       TYPE(CRTM_ChannelInfo_type)
                        DIMENSION:  Scalar
                        ATTRIBUTES: INTENT(IN OUT)
 
  OPTIONAL INPUTS:
        Channel_Subset: An integer array containing the subset list of channels.
                        Future calls to the CRTM main functions using the passed
                        ChannelInfo object will process ONLY the channels
                        specified in this list.
                        *** NOTE: This argument is ignored if the Reset optional
                        *** argument is specified with a .TRUE. value.            
                        UNITS:      N/A
                        TYPE:       INTEGER
                        DIMENSION:  Rank-1
                        ATTRIBUTES: INTENT(IN), OPTIONAL
 
        Reset:          Logical flag to reset the ChannelInfo object channel
                        processing subset to ALL channels.
                        If == .TRUE.  Future calls to the CRTM main functions using
                                      the passed ChannelInfo object will process
                                      ALL the channels
                           == .FALSE. Procedure execution is equivalent to the Reset
                                      argument not being specified at all.
                        UNITS:      N/A
                        TYPE:       LOGICAL
                        DIMENSION:  Scalar
                        ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status:   The return value is an integer defining the error status.
                        The error codes are defined in the Message_Handler module.
                        If == SUCCESS the channel subset setting was sucessful
                           == FAILURE an error occurred
                        UNITS:      N/A
                        TYPE:       INTEGER
                        DIMENSION:  Scalar
 
  COMMENTS:
        - The ChannelInfo object can be modified by this procedure.
        - An error in this procedure will DISABLE processing for ALL channels.
 
  \end{alltt}
