\subsection{\texttt{CRTM\_Allocate\_ChannelInfo} interface}
  \label{sec:CRTM_Allocate_ChannelInfo_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Allocate_ChannelInfo
  
  PURPOSE:
        Function to allocate the pointer members of a CRTM ChannelInfo
        data structure.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_Allocate_ChannelInfo( n_Channels             , &
                                                  ChannelInfo            , &
                                                  Message_Log=Message_Log  )
 
  INPUT ARGUMENTS:
        n_Channels:   The number of channels in the ChannelInfo structure.
                      Must be > 0.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar or Rank-1 array
                      ATTRIBUTES: INTENT(IN)
 
  OUTPUT ARGUMENTS:
        ChannelInfo:  ChannelInfo structure with allocated pointer members
                      UNITS:      N/A
                      TYPE:       CRTM_ChannelInfo_type
                      DIMENSION:  Same as input n_Channels argument
                      ATTRIBUTES: INTENT(IN OUT)
 
  OPTIONAL INPUT ARGUMENTS:
        Message_Log:  Character string specifying a filename in which any
                      Messages will be logged. If not specified, or if an
                      error occurs opening the log file, the default action
                      is to output Messages to standard output.
                      UNITS:      N/A
                      TYPE:       CHARACTER(*)
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status: The return value is an integer defining the error status.
                      The error codes are defined in the ERROR_HANDLER module.
                      If == SUCCESS the structure pointer allocations were
                                    successful
                         == FAILURE - an error occurred, or
                                    - the structure internal allocation counter
                                      is not equal to one (1) upon exiting this
                                      function. This value is incremented and
                                      decremented for every structure allocation
                                      and deallocation respectively.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
 
  COMMENTS:
        Note the INTENT on the output ChannelInfo argument is IN OUT rather than
        just OUT. This is necessary because the argument may be defined upon
        input. To prevent memory leaks, the IN OUT INTENT is a must.
 
  \end{alltt}
