\subsection{\texttt{CRTM\_Associated\_ChannelInfo} interface}
  \label{sec:CRTM_Associated_ChannelInfo_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Associated_ChannelInfo
 
  PURPOSE:
        Function to test the association status of the pointer members of a
        CRTM ChannelInfo structure.
 
  CALLING SEQUENCE:
        Association_Status = CRTM_Associated_ChannelInfo( ChannelInfo      , &
                                                          ANY_Test=Any_Test  )
 
  INPUT ARGUMENTS:
        ChannelInfo: ChannelInfo structure which is to have its pointer
                     member's association status tested.
                     UNITS:      N/A
                     TYPE:       CRTM_ChannelInfo_type
                     DIMENSION:  Scalar OR Rank-1 array
                     ATTRIBUTES: INTENT(IN)
 
  OPTIONAL INPUT ARGUMENTS:
        ANY_Test:    Set this argument to test if ANY of the
                     ChannelInfo structure pointer members are associated.
                     The default is to test if ALL the pointer members
                     are associated.
                     If ANY_Test = 0, test if ALL the pointer members
                                      are associated.  (DEFAULT)
                        ANY_Test = 1, test if ANY of the pointer members
                                      are associated.
 
  FUNCTION RESULT:
        Association_Status:  The return value is a logical value indicating the
                             association status of the ChannelInfo pointer
                             members.
                             .TRUE.  - if ALL the ChannelInfo pointer members
                                       are associated, or if the ANY_Test argument
                                       is set and ANY of the ChannelInfo
                                       pointer members are associated.
                             .FALSE. - some or all of the ChannelInfo pointer
                                       members are NOT associated.
                             UNITS:      N/A
                             TYPE:       LOGICAL
                             DIMENSION:  Same as input ChannelInfo argument
 
  \end{alltt}
