\subsection{\texttt{CRTM\_Forward} interface}
  \label{sec:CRTM_Forward_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Forward
 
  PURPOSE:
        Function that calculates top-of-atmosphere (TOA) radiances
        and brightness temperatures for an input atmospheric profile or
        profile set and user specified satellites/channels.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_Forward( Atmosphere       , &
                                     Surface          , &
                                     Geometry         , &
                                     ChannelInfo      , &
                                     RTSolution       , &
                                     Options = Options  )
 
  INPUTS:
        Atmosphere:     Structure containing the Atmosphere data.
                        UNITS:      N/A
                        TYPE:       CRTM_Atmosphere_type
                        DIMENSION:  Rank-1 (n_Profiles)
                        ATTRIBUTES: INTENT(IN)
 
        Surface:        Structure containing the Surface data.
                        UNITS:      N/A
                        TYPE:       CRTM_Surface_type
                        DIMENSION:  Same as input Atmosphere structure
                        ATTRIBUTES: INTENT(IN)
 
        Geometry:       Structure containing the view geometry
                        information.
                        UNITS:      N/A
                        TYPE:       CRTM_Geometry_type
                        DIMENSION:  Same as input Atmosphere structure
                        ATTRIBUTES: INTENT(IN)
 
        ChannelInfo:    Structure returned from the CRTM_Init() function
                        that contains the satellite/sensor channel index
                        information.
                        UNITS:      N/A
                        TYPE:       CRTM_ChannelInfo_type
                        DIMENSION:  Rank-1 (n_Sensors)
                        ATTRIBUTES: INTENT(IN)
 
  OUTPUTS:
        RTSolution:     Structure containing the soluition to the RT equation
                        for the given inputs.
                        UNITS:      N/A
                        TYPE:       CRTM_RTSolution_type
                        DIMENSION:  Rank-2 (n_Channels x n_Profiles)
                        ATTRIBUTES: INTENT(IN OUT)
 
  OPTIONAL INPUTS:
        Options:        Options structure containing the optional arguments
                        for the CRTM.
                        UNITS:      N/A
                        TYPE:       CRTM_Options_type
                        DIMENSION:  Same as input Atmosphere structure
                        ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status:   The return value is an integer defining the error status.
                        The error codes are defined in the Message_Handler module.
                        If == SUCCESS the computation was sucessful
                           == FAILURE an unrecoverable error occurred
                        UNITS:      N/A
                        TYPE:       INTEGER
                        DIMENSION:  Scalar
 
  COMMENTS:
        - The Options optional input structure argument contains
          spectral information (e.g. emissivity) that must have the same
          spectral dimensionality (the "L" dimension) as the output
          RTSolution structure.
 
  \end{alltt}
