\subsection{\texttt{CRTM\_Associated\_RTSolution} interface}
  \label{sec:CRTM_Associated_RTSolution_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Associated_RTSolution
 
  PURPOSE:
        Function to test the association status of the pointer members of a
        CRTM_RTSolution structure.
 
  CALLING SEQUENCE:
        Association_Status = CRTM_Associated_RTSolution( RTSolution       , &
                                                         ANY_Test=Any_Test  )
 
  INPUT ARGUMENTS:
        RTSolution:          RTSolution structure which is to have its pointer
                             member's association status tested.
                             UNITS:      N/A
                             TYPE:       CRTM_RTSolution_type
                             DIMENSION:  Scalar, Rank-1, OR Rank-2 array
                             ATTRIBUTES: INTENT(IN)
 
 
  OPTIONAL INPUT ARGUMENTS:
        ANY_Test:            Set this argument to test if ANY of the
                             CRTM_SfcOptics structure pointer members are associated.
                             The default is to test if ALL the pointer members
                             are associated.
                             If ANY_Test = 0, test if ALL the pointer members
                                              are associated.  (DEFAULT)
                                ANY_Test = 1, test if ANY of the pointer members
                                              are associated.
                             UNITS:      N/A
                             TYPE:       INTEGER
                             DIMENSION:  Scalar
                             ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Association_Status:  The return value is a logical value indicating the
                             association status of the RTSolution pointer
                             members.
                             .TRUE.  - if ALL the RTSolution pointer members
                                       are associated, or if the ANY_Test argument
                                       is set and ANY of the RTSolution
                                       pointer members are associated.
                             .FALSE. - some or all of the RTSolution pointer
                                       members are NOT associated.
                             UNITS:      N/A
                             TYPE:       LOGICAL
                             DIMENSION:  Same as input RTSolution argument
 
  \end{alltt}
