\subsection{\texttt{CRTM\_RTSolution\_WriteFile} interface}
  \label{sec:CRTM_RTSolution_WriteFile_interface}
  \begin{alltt}
 
  NAME:
        CRTM_RTSolution_WriteFile
 
  PURPOSE:
        Function to write CRTM RTSolution object files.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_RTSolution_WriteFile( Filename     , &
                                                  RTSolution   , &
                                                  Quiet = Quiet  )
 
  INPUTS:
        Filename:     Character string specifying the name of the
                      RTSolution format data file to write.
                      UNITS:      N/A
                      TYPE:       CHARACTER(*)
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN)
 
        RTSolution:   CRTM RTSolution object array containing the RTSolution
                      data.
                      UNITS:      N/A
                      TYPE:       CRTM_RTSolution_type
                      DIMENSION:  Rank-2 (n_Channels x n_Profiles)
                      ATTRIBUTES: INTENT(IN)
 
  OPTIONAL INPUTS:
        Quiet:        Set this logical argument to suppress INFORMATION
                      messages being printed to stdout
                      If == .FALSE., INFORMATION messages are OUTPUT [DEFAULT].
                         == .TRUE.,  INFORMATION messages are SUPPRESSED.
                      If not specified, default is .FALSE.
                      UNITS:      N/A
                      TYPE:       LOGICAL
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status: The return value is an integer defining the error status.
                      The error codes are defined in the Message_Handler module.
                      If == SUCCESS, the file write was successful
                         == FAILURE, an unrecoverable error occurred.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
 
  SIDE EFFECTS:
        - If the output file already exists, it is overwritten.
        - If an error occurs during *writing*, the output file is deleted before
          returning to the calling routine.
 
  \end{alltt}
