\subsection{\texttt{CRTM\_Allocate\_RTSolution} interface}
  \label{sec:CRTM_Allocate_RTSolution_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Allocate_RTSolution
  
  PURPOSE:
        Function to allocate the pointer members of the CRTM RTSolution
        data structure.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_Allocate_RTSolution( n_Layers               , &
                                                 RTSolution             , &
                                                 Message_Log=Message_Log  )
 
  INPUT ARGUMENTS:
        n_Layers:     Number of atmospheric layers 
                      Must be > 0
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN)
 
  OUTPUT ARGUMENTS:
        RTSolution:   RTSolution structure with allocated pointer members.
                      Upon allocation, all pointer members are initialized to
                      a value of zero.
 
                      The following chart shows the allowable dimension
                      combinations for the calling routine, where
                        L == number of channels
                        M == number of profiles
 
                         Input           Output
                        n_Layers       RTSolution
                        dimension      dimension
                      -------------------------------
                         scalar         scalar
                         scalar      Rank-1 (L or M)
                         scalar      Rank-2 (L x M)
 
                      These multiple interfaces are supplied purely for ease of
                      use depending on how it's used.
                      UNITS:      N/A
                      TYPE:       CRTM_RTSolution_type
                      DIMENSION:  Scalar, Rank-1, or Rank-2
                      ATTRIBUTES: INTENT(IN OUT)
 
  OPTIONAL INPUT ARGUMENTS:
        Message_Log:  Character string specifying a filename in which any
                      messages will be logged. If not specified, or if an
                      error occurs opening the log file, the default action
                      is to output messages to standard output.
                      UNITS:      N/A
                      TYPE:       CHARACTER(*)
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status: The return value is an integer defining the error status.
                      The error codes are defined in the Message_Handler module.
                      If == SUCCESS the structure re-initialisation was successful
                         == FAILURE - an error occurred, or
                                    - the structure internal allocation counter
                                      is not equal to one (1) upon exiting this
                                      function. This value is incremented and
                                      decremented for every structure allocation
                                      and deallocation respectively.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
 
  COMMENTS:
        Note the INTENT on the output RTSolution argument is IN OUT rather than
        just OUT. This is necessary because the argument may be defined upon
        input. To prevent memory leaks, the IN OUT INTENT is a must.
 
  \end{alltt}
