\subsection{\texttt{Create} interface}
  \label{sec:Create_interface}
  \begin{alltt}
 
  NAME:
    Create
 
  PURPOSE:
    Elemental subroutine method to create instances of CloudCover objects.
 
  CALLING SEQUENCE:
    CALL cc_obj%Create( n_Layers, &
                        Forward       = Forward, &
                        Error_Message = Error_Message )
 
  OBJECTS:
    cc_obj:         Cloud cover object
                    UNITS:      N/A
                    CLASS:      CRTM_CloudCover_type
                    DIMENSION:  Scalar or any rank
                    ATTRIBUTES: INTENT(OUT)
 
  INPUTS:
    n_Layers:       Number of layers for which there is cloud data.
                    Must be > 0.
                    UNITS:      N/A
                    TYPE:       INTEGER
                    DIMENSION:  Conformable with object.
                    ATTRIBUTES: INTENT(IN)
 
  OPTIONAL INPUTS:
    Forward:        Set this optional logical flag to allocate the sub-object to
                    hold the intermediate forward model results.
                    IF .FALSE. - the subobject is NOT allocated [DEFAULT]
                       .TRUE.  - the subobject is allocated
                    UNITS:      N/A
                    TYPE:       CHARACTER(*)
                    DIMENSION:  Conformable with object.
                    ATTRIBUTES: INTENT(IN), OPTIONAL
 
  OPTIONAL OUTPUTS:
    Error_Message:  If an error occurred creating the object, this
                    argument will contain error information.
                    UNITS:      N/A
                    TYPE:       CHARACTER(*)
                    DIMENSION:  Conformable with object.
                    ATTRIBUTES: INTENT(OUT), OPTIONAL
 
  \end{alltt}
