\subsection{\texttt{CRTM\_AOD\_AD} interface}
  \label{sec:CRTM_AOD_AD_interface}
  \begin{alltt}
 
  NAME:
        CRTM_AOD_AD
 
  PURPOSE:
        Function that calculates the adjoint nadir aerosol optical depth.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_AOD_AD( Atmosphere       , &
                                    RTSolution_AD    , &
                                    ChannelInfo      , &
                                    RTSolution       , &
                                    Atmosphere_AD    , &
                                    Options = Options  )
 
  INPUTS:
        Atmosphere:     Structure containing the Atmosphere data.
                        UNITS:      N/A
                        TYPE:       CRTM_Atmosphere_type
                        DIMENSION:  Rank-1 (n_Profiles)
                        ATTRIBUTES: INTENT(IN)
 
        RTSolution_AD:  Structure containing the RT solution adjoint inputs.
                        **NOTE: On EXIT from this function, the contents of
                                this structure may be modified (e.g. set to
                                zero.)
                        UNITS:      N/A
                        TYPE:       CRTM_RTSolution_type
                        DIMENSION:  Rank-2 (n_Channels x n_Profiles)
                        ATTRIBUTES: INTENT(IN OUT)
 
        ChannelInfo:    Structure returned from the CRTM_Init() function
                        that contains the satellite/sensor channel index
                        information.
                        UNITS:      N/A
                        TYPE:       CRTM_ChannelInfo_type
                        DIMENSION:  Rank-1 (n_Sensors)
                        ATTRIBUTES: INTENT(IN)
 
  OUTPUTS:
        RTSolution:     Structure containing the soluition to the RT equation
                        for the given inputs.
                        UNITS:      N/A
                        TYPE:       CRTM_RTSolution_type
                        DIMENSION:  Rank-2 (n_Channels x n_Profiles)
                        ATTRIBUTES: INTENT(IN OUT)
 
        Atmosphere_AD:  Structure containing the adjoint Atmosphere data.
                        **NOTE: On ENTRY to this function, the contents of
                                this structure should be defined (e.g.
                                initialized to some value based on the
                                position of this function in the call chain.)
                        UNITS:      N/A
                        TYPE:       CRTM_Atmosphere_type
                        DIMENSION:  Same as input Atmosphere argument
                        ATTRIBUTES: INTENT(IN OUT)
 
  OPTIONAL INPUTS:
        Options:        Options structure containing the optional arguments
                        for the CRTM.
                        UNITS:      N/A
                        TYPE:       CRTM_Options_type
                        DIMENSION:  Same as input Atmosphere structure
                        ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status:   The return value is an integer defining the error status.
                        The error codes are defined in the Message_Handler module.
                        If == SUCCESS the computation was sucessful
                           == FAILURE an unrecoverable error occurred
                        UNITS:      N/A
                        TYPE:       INTEGER
                        DIMENSION:  Scalar
 
  COMMENTS:
        - Many of the components of the Options optional input structure
          are not used in this function. Consult the CRTM User Guide for
          which Options components are usable for AOD calculations.
 
  \end{alltt}
