\subsection{\texttt{CRTM\_Atmosphere\_ReadFile} interface}
  \label{sec:CRTM_Atmosphere_ReadFile_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Atmosphere_ReadFile
 
  PURPOSE:
        Function to read CRTM Atmosphere object files.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_Atmosphere_ReadFile( Filename                , &
                                                 Atmosphere              , &
                                                 Quiet      = Quiet      , &
                                                 n_Channels = n_Channels , &
                                                 n_Profiles = n_Profiles , &
 
  INPUTS:
        Filename:     Character string specifying the name of an
                      Atmosphere format data file to read.
                      UNITS:      N/A
                      TYPE:       CHARACTER(*)
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN)
 
  OUTPUTS:
        Atmosphere:   CRTM Atmosphere object array containing the Atmosphere
                      data. Note the following meanings attributed to the
                      dimensions of the object array:
                      Rank-1: M profiles.
                              Only profile data are to be read in. The file
                              does not contain channel information. The
                              dimension of the structure is understood to
                              be the PROFILE dimension.
                      Rank-2: L channels  x  M profiles
                              Channel and profile data are to be read in.
                              The file contains both channel and profile
                              information. The first dimension of the
                              structure is the CHANNEL dimension, the second
                              is the PROFILE dimension. This is to allow
                              K-matrix structures to be read in with the
                              same function.
                      UNITS:      N/A
                      TYPE:       CRTM_Atmosphere_type
                      DIMENSION:  Rank-1 (M) or Rank-2 (L x M)
                      ATTRIBUTES: INTENT(OUT)
 
  OPTIONAL INPUTS:
        Quiet:        Set this logical argument to suppress INFORMATION
                      messages being printed to stdout
                      If == .FALSE., INFORMATION messages are OUTPUT [DEFAULT].
                         == .TRUE.,  INFORMATION messages are SUPPRESSED.
                      If not specified, default is .FALSE.
                      UNITS:      N/A
                      TYPE:       LOGICAL
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN), OPTIONAL
 
  OPTIONAL OUTPUTS:
        n_Channels:   The number of channels for which data was read. Note that
                      this value will always be 0 for a profile-only dataset--
                      it only has meaning for K-matrix data.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
                      ATTRIBUTES: OPTIONAL, INTENT(OUT)
 
        n_Profiles:   The number of profiles for which data was read.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
                      ATTRIBUTES: OPTIONAL, INTENT(OUT)
 
 
  FUNCTION RESULT:
        Error_Status: The return value is an integer defining the error status.
                      The error codes are defined in the Message_Handler module.
                      If == SUCCESS, the file read was successful
                         == FAILURE, an unrecoverable error occurred.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
 
  \end{alltt}
