\subsection{\texttt{CRTM\_Assign\_Surface} interface}
  \label{sec:CRTM_Assign_Surface_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Assign_Surface
 
  PURPOSE:
        Function to copy valid Surface structures.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_Assign_Surface( Surface_in             , &
                                            Surface_out            , &
                                            Message_Log=Message_Log  )
 
  INPUT ARGUMENTS:
        Surface_in:   Surface structure which is to be copied. In the context of
                      the CRTM, rank-1 corresponds to an vector of profiles,
                      and rank-2 corresponds to an array of channels x profiles.
                      The latter is used in the K-matrix model.
                      UNITS:      N/A
                      TYPE:       CRTM_Surface_type
                      DIMENSION:  Scalar, Rank-1, OR Rank-2 array
                      ATTRIBUTES: INTENT(IN)
 
  OUTPUT ARGUMENTS:
        Surface_out:  Copy of the input structure, Surface_in.
                      UNITS:      N/A
                      TYPE:       CRTM_Surface_type
                      DIMENSION:  Same as Surface_in
                      ATTRIBUTES: INTENT(IN OUT)
 
  OPTIONAL INPUT ARGUMENTS:
        Message_Log:  Character string specifying a filename in which any
                      messages will be logged. If not specified, or if an
                      error occurs opening the log file, the default action
                      is to output messages to standard output.
                      UNITS:      N/A
                      TYPE:       CHARACTER(*)
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status: The return value is an integer defining the error status.
                      The error codes are defined in the Message_Handler module.
                      If == SUCCESS the structure assignment was successful
                         == FAILURE an error occurred
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
 
  COMMENTS:
        Note the INTENT on the output Surface argument is IN OUT rather than
        just OUT. This is necessary because the argument may be defined upon
        input. To prevent memory leaks, the IN OUT INTENT is a must.
 
  \end{alltt}
