\subsection{\texttt{CRTM\_Write\_Surface\_Binary} interface}
  \label{sec:CRTM_Write_Surface_Binary_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Write_Surface_Binary
 
  PURPOSE:
        Function to write Binary format Surface files.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_Write_Surface_Binary( Filename               , &
                                                  Surface                , &
                                                  Quiet      =Quiet      , &
                                                  RCS_Id     =RCS_Id     , &
                                                  Message_Log=Message_Log  )
 
  INPUT ARGUMENTS:
        Filename:     Character string specifying the name of an output
                      Surface format data file.
                      UNITS:      N/A
                      TYPE:       CHARACTER(*)
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN)
 
        Surface:      Structure containing the Surface data to write.
                      Note the following meanings attributed to the
                      dimensions of the structure array:
                      Rank-1: M profiles.
                              Only profile data are to be read in. The file
                              does not contain channel information. The
                              dimension of the structure is understood to
                              be the PROFILE dimension.
                      Rank-2: L channels  x  M profiles
                              Channel and profile data are to be read in.
                              The file contains both channel and profile
                              information. The first dimension of the 
                              structure is the CHANNEL dimension, the second
                              is the PROFILE dimension. This is to allow
                              K-matrix structures to be read in with the
                              same function.
                      UNITS:      N/A
                      TYPE:       CRTM_Surface_type
                      DIMENSION:  Rank-1 (M) or Rank-2 (L x M)
                      ATTRIBUTES: INTENT(IN)
 
  OPTIONAL INPUT ARGUMENTS:
        Quiet:        Set this argument to suppress INFORMATION messages
                      being printed to standard output (or the message
                      log file if the Message_Log optional argument is
                      used.) By default, INFORMATION messages are printed.
                      If QUIET = 0, INFORMATION messages are OUTPUT.
                         QUIET = 1, INFORMATION messages are SUPPRESSED.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN), OPTIONAL
 
        Message_Log:  Character string specifying a filename in which any
                      messages will be logged. If not specified, or if an
                      error occurs opening the log file, the default action
                      is to output messages to standard output.
                      UNITS:      N/A
                      TYPE:       CHARACTER(*)
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN), OPTIONAL
 
  OPTIONAL OUTPUT ARGUMENTS:
        RCS_Id:       Character string containing the version control Id
                      field for the module.
                      UNITS:      N/A
                      TYPE:       CHARACTER(*)
                      DIMENSION:  Scalar
                      ATTRIBUTES: OPTIONAL, INTENT(OUT)
 
  FUNCTION RESULT:
        Error_Status: The return value is an integer defining the error status.
                      The error codes are defined in the Message_Handler module.
                      If == SUCCESS the Binary file write was successful
                         == FAILURE an unrecoverable error occurred.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
 
  SIDE EFFECTS:
        - If the output file already exists, it is overwritten.
        - If an error occurs *during* the write phase, the output file is deleted
          before returning to the calling routine.
 
  \end{alltt}
