\subsection{\texttt{CRTM\_Destroy\_Surface} interface}
  \label{sec:CRTM_Destroy_Surface_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Destroy_Surface
  
  PURPOSE:
        Function to re-initialize the scalar and pointer members of Surface
        data structures.
 
        NOTE: This function is mostly a wrapper for the CRTM_SensorData
              destruction routine to provide the functionality and convenience
              of allocation of both scalar and rank-1 Surface structures in
              the same manner as for CRTM_Atmosphere_type structures.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_Destroy_Surface( Surface                , &
                                             Message_Log=Message_Log  )
 
  OUTPUT ARGUMENTS:
        Surface:      Re-initialized Surface structure. In the context of
                      the CRTM, rank-1 corresponds to an vector of profiles,
                      and rank-2 corresponds to an array of channels x profiles.
                      The latter is used in the K-matrix model.
                      UNITS:      N/A
                      TYPE:       CRTM_Surface_type
                      DIMENSION:  Scalar, Rank-1, OR Rank-2 array
                      ATTRIBUTES: INTENT(IN OUT)
 
  OPTIONAL INPUT ARGUMENTS:
        Message_Log:  Character string specifying a filename in which any
                      messages will be logged. If not specified, or if an
                      error occurs opening the log file, the default action
                      is to output messages to standard output.
                      UNITS:      N/A
                      TYPE:       CHARACTER(*)
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status: The return value is an integer defining the error status.
                      The error codes are defined in the Message_Handler module.
                      If == SUCCESS the structure re-initialisation was successful
                         == FAILURE - an error occurred, or
                                    - the structure internal allocation counter
                                      is not equal to zero (0) upon exiting this
                                      function. This value is incremented and
                                      decremented for every structure allocation
                                      and deallocation respectively.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
 
  COMMENTS:
        Note the INTENT on the output Surface argument is IN OUT rather than
        just OUT. This is necessary because the argument may be defined upon
        input. To prevent memory leaks, the IN OUT INTENT is a must.
 
  \end{alltt}
