\subsection{\texttt{LBLRTM\_Phdr\_Read} interface}
  \label{sec:LBLRTM_Phdr_Read_interface}
  \begin{alltt}
 
  NAME:
        LBLRTM_Phdr_Read
 
  PURPOSE:
        Function to read an LBLRTM panel header from an LBLRTM format
        file.
 
  CALLING SEQUENCE:
        Error_Status = LBLRTM_Phdr_Read( &
                         LBLRTM_Phdr, &
                         FileId     , &
                         EOF          )
 
  OBJECTS:
        LBLRTM_Phdr:  LBLRTM panel header object to hold the data.
                      UNITS:      N/A
                      TYPE:       LBLRTM_Phdr_type
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(OUT)
 
  INPUTS:
        FileId:       The unit number for the already open LBLRTM file.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN)
 
  OUTPUTS:
        EOF:          Integer flag indicating end-of-file status for the
                      LBLRTM format file after the read. Valid return values
                      are defined in the LBLRTM_Parameters module.
                      If == LBLRTM_FILE_EOF:   End-Of-File has been reached.
                                               The file is then closed.
                         == LBLRTM_FILE_EOL:   End-Of-Layer has been reached.
                                               In this case, the next read
                                               should be of the file header
                                               for the (possible) next layer.
                         == LBLRTM_FILE_OK:    No EOF or EOL condition. The
                                               next read should be the panel
                                               data.
                         == LBLRTM_FILE_UNDEF: An error occurred. The file is
                                               closed.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(OUT)
 
  FUNCTION RESULT:
        Error_Status: The return value is an integer defining the error status.
                      The error codes are defined in the Message_Handler module.
                      If == SUCCESS the LBLRTM panel header read was successful
                         == FAILURE an error occurred
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
 
  SIDE EFFECTS:
        If an error occurs or the end-of-file is encountered, the input file is
        closed.
 
  \end{alltt}
