\subsection{\texttt{CRTM\_Options\_ReadFile} interface}
  \label{sec:CRTM_Options_ReadFile_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Options_ReadFile
 
  PURPOSE:
        Function to read CRTM Options object files.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_Options_ReadFile( &
                         Filename               , &
                         Options                , &
                         Quiet      = Quiet     , &
                         n_Profiles = n_Profiles  )
 
  INPUTS:
        Filename:     Character string specifying the name of an
                      Options format data file to read.
                      UNITS:      N/A
                      TYPE:       CHARACTER(*)
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN)
 
  OUTPUTS:
        Options:      CRTM Options object array containing the Options
                      data.
                      UNITS:      N/A
                      TYPE:       CRTM_Options_type
                      DIMENSION:  Rank-1 (n_Profiles)
                      ATTRIBUTES: INTENT(OUT)
 
  OPTIONAL INPUTS:
        Quiet:        Set this logical argument to suppress INFORMATION
                      messages being printed to stdout
                      If == .FALSE., INFORMATION messages are OUTPUT [DEFAULT].
                         == .TRUE.,  INFORMATION messages are SUPPRESSED.
                      If not specified, default is .FALSE.
                      UNITS:      N/A
                      TYPE:       LOGICAL
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN), OPTIONAL
 
  OPTIONAL OUTPUTS:
        n_Profiles:   The number of profiles for which data was read.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
                      ATTRIBUTES: OPTIONAL, INTENT(OUT)
 
 
  FUNCTION RESULT:
        Error_Status: The return value is an integer defining the error status.
                      The error codes are defined in the Message_Handler module.
                      If == SUCCESS, the file read was successful
                         == FAILURE, an unrecoverable error occurred.
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
 
  \end{alltt}
