\subsection{\texttt{CRTM\_Equal\_Atmosphere} interface}
  \label{sec:CRTM_Equal_Atmosphere_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Equal_Atmosphere
 
  PURPOSE:
        Function to test if two Atmosphere structures are equal.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_Equal_Atmosphere( Atmosphere_LHS                       , &
                                              Atmosphere_RHS                       , &
                                              ULP_Scale         =ULP_Scale         , &
                                              Percent_Difference=Percent_Difference, &
                                              Check_All         =Check_All         , &
                                              Message_Log       =Message_Log         )
 
 
  INPUT ARGUMENTS:
        Atmosphere_LHS:     Atmosphere structure to be compared; equivalent to the
                            left-hand side of a lexical comparison, e.g.
                              IF ( Atmosphere_LHS == Atmosphere_RHS ).
                            In the context of the CRTM, rank-1 corresponds to an
                            vector of profiles, and rank-2 corresponds to an array
                            of channels x profiles. The latter is used in the
                            K-matrix model.
                            UNITS:      N/A
                            TYPE:       CRTM_Atmosphere_type
                            DIMENSION:  Scalar, Rank-1, or Rank-2 array
                            ATTRIBUTES: INTENT(IN)
 
        Atmosphere_RHS:     Atmosphere structure to be compared to; equivalent to
                            right-hand side of a lexical comparison, e.g.
                              IF ( Atmosphere_LHS == Atmosphere_RHS ).
                            UNITS:      N/A
                            TYPE:       CRTM_Atmosphere_type
                            DIMENSION:  Same as Atmosphere_LHS
                            ATTRIBUTES: INTENT(IN)
 
  OPTIONAL INPUT ARGUMENTS:
        ULP_Scale:          Unit of data precision used to scale the floating
                            point comparison. ULP stands for "Unit in the Last Place,"
                            the smallest possible increment or decrement that can be
                            made using a machine's floating point arithmetic.
                            Value must be positive - if a negative value is supplied,
                            the absolute value is used. If not specified, the default
                            value is 1.
                            UNITS:      N/A
                            TYPE:       INTEGER
                            DIMENSION:  Scalar
                            ATTRIBUTES: INTENT(IN), OPTIONAL
 
        Percent_Differnece: Percentage difference value to use in comparing
                            the numbers rather than testing within some numerical
                            limit. The ULP_Scale argument is ignored if this argument is
                            specified.
                            UNITS:      N/A
                            TYPE:       REAL(fp)
                            DIMENSION:  Scalar
                            ATTRIBUTES: OPTIONAL, INTENT(IN)
 
        Check_All:          Set this argument to check ALL the floating point
                            channel data of the Atmosphere structures. The default
                            action is return with a FAILURE status as soon as
                            any difference is found. This optional argument can
                            be used to get a listing of ALL the differences
                            between data in Atmosphere structures.
                            If == 0, Return with FAILURE status as soon as
                                     ANY difference is found  *DEFAULT*
                               == 1, Set FAILURE status if ANY difference is
                                     found, but continue to check ALL data.
                            UNITS:      N/A
                            TYPE:       INTEGER
                            DIMENSION:  Scalar
                            ATTRIBUTES: INTENT(IN), OPTIONAL
 
        Message_Log:        Character string specifying a filename in which any
                            messages will be logged. If not specified, or if an
                            error occurs opening the log file, the default action
                            is to output messages to standard output.
                            UNITS:      None
                            TYPE:       CHARACTER(*)
                            DIMENSION:  Scalar
                            ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status:       The return value is an integer defining the error status.
                            The error codes are defined in the Message_Handler module.
                            If == SUCCESS the structures were equal
                               == FAILURE - an error occurred, or
                                          - the structures were different.
                            UNITS:      N/A
                            TYPE:       INTEGER
                            DIMENSION:  Scalar
 
  \end{alltt}
