\subsection{\texttt{CRTM\_Assign\_Cloud} interface}
  \label{sec:CRTM_Assign_Cloud_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Assign_Cloud
 
  PURPOSE:
        Function to copy valid CRTM_Cloud structures.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_Assign_Cloud( Cloud_in               , &
                                          Cloud_out              , &
                                          Message_Log=Message_Log  )
 
  INPUT ARGUMENTS:
        Cloud_in:      Cloud structure which is to be copied.
                       UNITS:      N/A
                       TYPE:       CRTM_Cloud_type
                       DIMENSION:  Scalar or Rank-1 array
                       ATTRIBUTES: INTENT(IN)
 
  OUTPUT ARGUMENTS:
        Cloud_out:     Copy of the input structure, Cloud_in.
                       UNITS:      N/A
                       TYPE:       CRTM_Cloud_type
                       DIMENSION:  Same as Cloud_in argument
                       ATTRIBUTES: INTENT(IN OUT)
 
  OPTIONAL INPUT ARGUMENTS:
        Message_Log:   Character string specifying a filename in which any
                       messages will be logged. If not specified, or if an
                       error occurs opening the log file, the default action
                       is to output messages to standard output.
                       UNITS:      N/A
                       TYPE:       CHARACTER(*)
                       DIMENSION:  Scalar
                       ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status:  The return value is an integer defining the error status.
                       The error codes are defined in the Message_Handler module.
                       If == SUCCESS the structure assignment was successful
                          == FAILURE an error occurred
                       UNITS:      N/A
                       TYPE:       INTEGER
                       DIMENSION:  Scalar
 
  COMMENTS:
        Note the INTENT on the output Cloud argument is IN OUT rather than
        just OUT. This is necessary because the argument may be defined upon
        input. To prevent memory leaks, the IN OUT INTENT is a must.
 
  \end{alltt}
