\subsection{\texttt{CRTM\_SetLayers\_Atmosphere} interface}
  \label{sec:CRTM_SetLayers_Atmosphere_interface}
  \begin{alltt}
 
  NAME:
        CRTM_SetLayers_Atmosphere
  
  PURPOSE:
        Function to set the number of layers to use in a CRTM Atmosphere
        structure.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_SetLayers_Atmosphere( n_Layers  , &
                                                  Atmosphere  )
 
  INPUTS:
        n_Layers:     The value to set the n_Layers component of the 
                      Atmosphere structure, as well as any of its
                      Cloud or Aerosol structure components.
                      UNITS:      N/A
                      TYPE:       CRTM_Atmosphere_type
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN)
 
        Atmosphere:   Atmosphere structure in which the n_Layers dimension
                      is to be updated.
                      UNITS:      N/A
                      TYPE:       CRTM_Atmosphere_type
                      DIMENSION:  Scalar, Rank-1, or Rank-2 array
                      ATTRIBUTES: INTENT(IN OUT)
  OUTPUTS:
        Atmosphere:   On output, the atmosphere structure with the updated
                      n_Layers dimension.
                      UNITS:      N/A
                      TYPE:       CRTM_Atmosphere_type
                      DIMENSION:  Scalar, Rank-1, or Rank-2 array
                      ATTRIBUTES: INTENT(IN OUT)
 
  FUNCTION RESULT:
        Error_Status: The return value is an integer defining the error status.
                      The error codes are defined in the Message_Handler module.
                      If == SUCCESS the layer reset was successful
                         == FAILURE an error occurred
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
 
  SIDE EFFECTS:
        The argument Atmosphere is INTENT(IN OUT) and is modified upon output.
 
  COMMENTS:
        - Note that the n_Layers input is *ALWAYS* scalar. Thus, all Atmosphere
          elements will be set to the same number of layers.
 
        - If n_Layers <= Atmosphere%Max_Layers, then only the dimension value
          of the structure and any sub-structures are changed.
 
        - If n_Layers > Atmosphere%Max_Layers, then the entire structure is
          reallocated to the required number of layers. No other dimensions
          of the structure or substructures are altered.
 
  \end{alltt}
