\subsection{\texttt{CRTM\_AddLayers\_Atmosphere} interface}
  \label{sec:CRTM_AddLayers_Atmosphere_interface}
  \begin{alltt}
 
  NAME:
        CRTM_AddLayers_Atmosphere
 
  PURPOSE:
        Function to copy an atmosphere structure and adding extra layers from
        climatology as required to supplement the upper atmosphere profile data.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_AddLayers_Atmosphere( Atm_In                 , &    Input
                                                  Atm_Out                , &    Output
                                                  Message_Log=Message_Log  )    Error messaging
 
  INPUT ARGUMENTS:
        Atm_In:          Atmosphere structure that is to be copied.
                         UNITS:      N/A
                         TYPE:       CRTM_Atmosphere_type
                         DIMENSION:  Scalar
                         ATTRIBUTES: INTENT(IN)
 
  OUTPUT ARGUMENTS:
        Atm_Out:         Copy of the input atmosphere structure with extra upper
                         atmosphere layers added as required.
                         UNITS:      N/A
                         TYPE:       CRTM_Atmosphere_type
                         DIMENSION:  Scalar
                         ATTRIBUTES: INTENT(IN OUT)
 
  OPTIONAL INPUT ARGUMENTS:
        Message_Log:     Character string specifying a filename in which any
                         messages will be logged. If not specified, or if an
                         error occurs opening the log file, the default action
                         is to output messages to standard output.
                         UNITS:      N/A
                         TYPE:       CHARACTER(*)
                         DIMENSION:  Scalar
                         ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status:    The return value is an integer defining the error status.
                         The error codes are defined in the Message_Handler module.
                         If == SUCCESS the operation was successful
                            == FAILURE an error occurred
                         UNITS:      N/A
                         TYPE:       INTEGER
                         DIMENSION:  Scalar
 
  COMMENTS:
        Note the INTENT on the output Atm_Out argument is IN OUT rather than
        just OUT. This is necessary because the argument may be defined upon
        input. To prevent memory leaks, the IN OUT INTENT is a must.
 
  \end{alltt}
