\subsection{\texttt{CRTM\_SetLayers\_Aerosol} interface}
  \label{sec:CRTM_SetLayers_Aerosol_interface}
  \begin{alltt}
 
  NAME:
        CRTM_SetLayers_Aerosol
  
  PURPOSE:
        Function to set the number of layers to use in a CRTM Aerosol
        structure.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_SetLayers_Aerosol( n_Layers               , &
                                               Aerosol                , &
                                               Message_Log=Message_Log  )
 
  INPUT ARGUMENTS:
        n_Layers:     The value to set the n_Layers component of the 
                      Aerosol structure, as well as those of any of its
                      structure components.
                      UNITS:      N/A
                      TYPE:       CRTM_Aerosol_type
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN)
 
        Aerosol:      Aerosol structure in which the n_Layers dimension
                      is to be updated.
                      UNITS:      N/A
                      TYPE:       CRTM_Aerosol_type
                      DIMENSION:  Scalar or Rank-1 array
                      ATTRIBUTES: INTENT(IN OUT)
  OUTPUT ARGUMENTS:
        Aerosol:      On output, the Aerosol structure with the updated
                      n_Layers dimension.
                      UNITS:      N/A
                      TYPE:       CRTM_Aerosol_type
                      DIMENSION:  Scalar or Rank-1 array
                      ATTRIBUTES: INTENT(IN OUT)
 
  OPTIONAL INPUT ARGUMENTS:
        Message_Log:  Character string specifying a filename in which any
                      messages will be logged. If not specified, or if an
                      error occurs opening the log file, the default action
                      is to output messages to standard output.
                      UNITS:      None
                      TYPE:       CHARACTER(*)
                      DIMENSION:  Scalar
                      ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status: The return value is an integer defining the error status.
                      The error codes are defined in the Message_Handler module.
                      If == SUCCESS the layer reset was successful
                         == FAILURE an error occurred
                      UNITS:      N/A
                      TYPE:       INTEGER
                      DIMENSION:  Scalar
 
  SIDE EFFECTS:
        The argument Aerosol is INTENT(IN OUT) and is modified upon output. The
        elements of the structureare reinitialised
 
  COMMENTS:
        - Note that the n_Layers input is *ALWAYS* scalar. Thus, all Aerosol
          elements will be set to the same number of layers.
 
        - If n_Layers <= Aerosol%Max_Layers, then only the dimension value
          of the structure and any sub-structures are changed.
 
        - If n_Layers > Aerosol%Max_Layers, then the entire structure is
          reallocated to the required number of layers.
 
  \end{alltt}
