\subsection{\texttt{CRTM\_Zero\_Atmosphere} interface}
  \label{sec:CRTM_Zero_Atmosphere_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Zero_Atmosphere
  
  PURPOSE:
        Subroutine to zero-out various members of a CRTM_Atmosphere structure -
        both scalar and pointer.
 
  CALLING SEQUENCE:
        CALL CRTM_Zero_Atmosphere( Atmosphere )
 
  OUTPUT ARGUMENTS:
        Atmosphere:   Zeroed out Atmosphere structure.
                      In the context of the CRTM, rank-1 corresponds to an
                      vector of profiles, and rank-2 corresponds to an array
                      of channels x profiles. The latter is used in the
                      K-matrix model.
                      UNITS:      N/A
                      TYPE:       CRTM_Atmosphere_type
                      DIMENSION:  Scalar, Rank-1, or Rank-2 array
                      ATTRIBUTES: INTENT(IN OUT)
 
  COMMENTS:
        - No checking of the input structure is performed, so there are no
          tests for component association status. This means the Atmosphere
          structure must have allocated components upon entry to this
          routine.
 
        - The dimension components of the structure are *NOT* set to zero.
 
        - The Absorber_ID and Absorber_Units components are *NOT* zeroed out
          in this routine.
 
        - Note the INTENT on the output Atmosphere argument is IN OUT rather than
          just OUT. This is necessary because the argument must be defined upon
          input.
 
  \end{alltt}
