\subsection{\texttt{CRTM\_Assign\_Atmosphere} interface}
  \label{sec:CRTM_Assign_Atmosphere_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Assign_Atmosphere
 
  PURPOSE:
        Function to copy valid CRTM Atmosphere structures.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_Assign_Atmosphere( Atmosphere_in          , &
                                               Atmosphere_out         , &
                                               Message_Log=Message_Log  )
 
  INPUT ARGUMENTS:
        Atmosphere_in:   Atmosphere structure which is to be copied. In the
                         context of the CRTM, rank-1 corresponds to an vector
                         of profiles, and rank-2 corresponds to an array of
                         channels x profiles. The latter is used in the K-matrix
                         model.
                         UNITS:      N/A
                         TYPE:       CRTM_Atmosphere_type
                         DIMENSION:  Scalar, Rank-1, or Rank-2 array
                         ATTRIBUTES: INTENT(IN)
 
  OUTPUT ARGUMENTS:
        Atmosphere_out:  Copy of the input structure, Atmosphere_in.
                         UNITS:      N/A
                         TYPE:       CRTM_Atmosphere_type
                         DIMENSION:  Same as Atmosphere_in
                         ATTRIBUTES: INTENT(IN OUT)
 
  OPTIONAL INPUT ARGUMENTS:
        Message_Log:     Character string specifying a filename in which any
                         messages will be logged. If not specified, or if an
                         error occurs opening the log file, the default action
                         is to output messages to standard output.
                         UNITS:      N/A
                         TYPE:       CHARACTER(*)
                         DIMENSION:  Scalar
                         ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status:    The return value is an integer defining the error status.
                         The error codes are defined in the Message_Handler module.
                         If == SUCCESS the structure assignment was successful
                            == FAILURE an error occurred
                         UNITS:      N/A
                         TYPE:       INTEGER
                         DIMENSION:  Scalar
 
  COMMENTS:
        Note the INTENT on the output Atmosphere argument is IN OUT rather than
        just OUT. This is necessary because the argument may be defined upon
        input. To prevent memory leaks, the IN OUT INTENT is a must.
 
  \end{alltt}
