\subsection{\texttt{CRTM\_Compute\_GeometryInfo} interface}
  \label{sec:CRTM_Compute_GeometryInfo_interface}
  \begin{alltt}
 
  NAME:
        CRTM_Compute_GeometryInfo
  
  PURPOSE:
        Function to compute the derived geometry from the user specified
        components of the CRTM_GeometryInfo structure.
 
  CALLING SEQUENCE:
        Error_Status = CRTM_Compute_GeometryInfo( GeometryInfo           , &
                                                  Message_Log=Message_Log  )
 
  INPUT ARGUMENTS:
        GeometryInfo:  The CRTM_GeometryInfo structure containing the user
                       defined inputs, in particular the angles.
                       UNITS:      N/A
                       TYPE:       CRTM_GeometryInfo_type
                       DIMENSION:  Scalar
                       ATTRIBUTES: INTENT(IN OUT)
 
  OUTPUT ARGUMENTS:
        GeometryInfo:  The CRTM_GeometryInfo structure with the derived
                       angle components filled..
                       UNITS:      N/A
                       TYPE:       CRTM_GeometryInfo_type
                       DIMENSION:  Scalar
                       ATTRIBUTES: INTENT(IN OUT)
 
  OPTIONAL INPUT ARGUMENTS:
        Message_Log:   Character string specifying a filename in which any
                       messages will be logged. If not specified, or if an
                       error occurs opening the log file, the default action
                       is to output messages to the screen.
                       UNITS:      N/A
                       TYPE:       CHARACTER( * )
                       DIMENSION:  Scalar
                       ATTRIBUTES: INTENT( IN ), OPTIONAL
 
  FUNCTION RESULT:
        Error_Status:   The return value is an integer defining the error status.
                        The error codes are defined in the ERROR_HANDLER module.
                        If == SUCCESS the computation was sucessful
                           == WARNING invalid data was found, but altered to default.
                           == FAILURE invalid data was found
                        UNITS:      N/A
                        TYPE:       INTEGER
                        DIMENSION:  Scalar
 
  SIDE EFFECTS:
        This function changes the values of the derived components of the
        GeometryInfo structure argument.
 
  \end{alltt}
