% The generic preamble
\input{preamble}

% Define included documents
\includeonly{Compilation.section,Create_TAPE3.section,Test_Case_Built_In.section, Test_Case_User_Defined.section,IBM_Compiler_issue.appendix,gfortran_Compiler_issue.appendix}


% Title info
\title{LBLRTM v11.3 Install and Test}
\author{Paul van Delst\email{paul.vandelst@noaa.gov}\\JCSDA/EMC/SAIC}
\date{October, 2008}
\docnumber{(unassigned)}
\docseries{CRTM}


%-------------------------------------------------------------------------------
%                            Ze document begins...
%-------------------------------------------------------------------------------
\begin{document}
\maketitle

%\draftwatermark


\section{Introduction}
%=====================
This document details the installation and testing of the LNFL v2.5 and LBLRTM v11.3 software with the HITRAN2004 AER v2.1 spectrosopic database on two systems: an Intel PC running Red Hat RHE4.0 linux and an IBM SP running AIX 5.3. All the original source code and datafiles were obtained from the AER, Inc. website: http://www.rtweb.aer.com.

Several example inputs and outputs are provided with the LBLRTM v11.3 distribution. In all cases, the tests were performed using both the locally generated \texttt{TAPE3} file (see section \ref{sec:local_tape3}) and the one supplied by AER. All the comparisons that follow are for the generated \texttt{TAPE27} files only where the computed radiances were converted to brightness temperatures and then differenced with the same for the AER-supplied \texttt{TAPE27\_ex} files.


% Include all the various sections
%=================================
\include{Compilation.section}
\include{Create_TAPE3.section}
\include{Test_Case_Built_In.section}
\include{Test_Case_User_Defined.section}

\section*{Acknowledgements}
%==========================
The LBLRTM software and associated data files are an integral part of our ability to use satellite radiances in the data assimilation systems at NCEP/EMC/JCSDA. So, thanks go to the people at AER, Inc. who provide and, importantly, maintain the LBLRTM source code and spectroscopic data inputs. Any list of inidividuals would be woefully short and incomplete but special thanks go to Jean-Luc Moncet, Vivienne Payne, and Mark Shephard of AER Inc., and Tony Clough of Clough Associates for their help.

% Appendix section
%=================
\begin{appendix}
  \include{gfortran_Compiler_issue.appendix}
  \include{IBM_Compiler_issue.appendix}
\end{appendix}

\end{document}

