\subsection{\texttt{Compute\_CloudCover} interface}
  \label{sec:Compute_CloudCover_interface}
  \begin{alltt}
 
  NAME:
    Compute_CloudCover
 
  PURPOSE:
    Function method to compute the cloud cover profile given a supplied
    Atmosphere object, and populate the CloudCover object with the
    results.
 
  CALLING SEQUENCE:
    err_stat = cc_obj%Compute_CloudCover( &
                 atmosphere       , &
                 Overlap = overlap  )
 
  OBJECTS:
    cc_obj:      Cloud cover object which is to be populated with cloud
                 cover results.
                 UNITS:      N/A
                 CLASS:      CRTM_CloudCover_type
                 DIMENSION:  Scalar
                 ATTRIBUTES: INTENT(OUT)
 
  INPUTS:
    atmosphere:  Atmopshere object containing the layer cloud fraction
                 profile, and the actual cloud profiles for when cloud
                 water content averaging of the cloud cover is selected.
                 UNITS:      N/A
                 TYPE:       CRTM_Atmosphere_type
                 DIMENSION:  Scalar
                 ATTRIBUTES: INTENT(IN)
 
  OPTIONAL INPUTS:
    overlap:     Set this argument to a flag defining the cloud coverage
                 algorithm used. Supplied module functions providing valid flag
                 output are:
                   CloudCover_Maximum_Overlap(): Use maximum overlap method.
                   CloudCover_Random_Overlap() : Use random overlap method.
                   CloudCover_MaxRan_Overlap() : Use maximum-random overlap method.
                   CloudCover_Average_Overlap(): Use cloud content weighted averaged method. [DEFAULT]
                 If not specified, the default is the cloud content weighted
                 averaged method
                 UNITS:      N/A
                 TYPE:       INTEGER
                 DIMENSION:  Scalar
                 ATTRIBUTES: INTENT(IN), OPTIONAL
 
  FUNCTION RESULT:
    err_stat:    The return value is an integer defining the error status.
                 The error codes are defined in the Message_Handler module.
                   If == SUCCESS, the computation was successful
                      == FAILURE, an unrecoverable error occurred.
                 UNITS:      N/A
                 TYPE:       INTEGER
                 DIMENSION:  Scalar
 
  \end{alltt}
